Analysis of cloud enhancement events in a 30-year record of global solar irradiance at Thessaloniki, Greece

### 2024-09-08 article/article.Rmd
Commit 2024-09-08 08:14

Figure\nobreakspace{}\ref{fig:P-energy} shows the time series of the yearly number of
CE cases (each with duration of one minute), the yearly mean OI and the yearly excess
irradiation for the period 1994 -- 2023, together with corresponding linear trends.
To account for missing data all three quantities have been divided with the fraction
of the valid GHI observations in each month.
All three quantities show increasing trends, most pronounced for the
frequency of occurrence 
($`r plus_sign(round(yearlyCE[var == "GLB_diff.N", slope], 0))`\pm `r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 0)`\,\text{cases}/\text{year}$)
and the excess irradiation 
($`r plus_sign(round(yearlyCE[var == "GLB_diff.sum", slope], 1))` \pm `r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kJ}/\text{year}$),
which are also statistically significant.
In contrast the trend of the yearly mean OI is negligible 
($`r plus_sign(round(yearlyCE[var == "GLB_diff.mean", slope], 2))`\pm `r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 1)`\,\text{W}/\text{m}^2/\text{year}$)
and of no statistical significance.
The average OI for the entire period is
$`r plus_sign(round(mean(ST_E_yearly$GLB_diff.mean), 1))`\pm `r round(sd(ST_E_yearly$GLB_diff.mean),1)`\,\text{W}/\text{m}^2$.
The interannual variability of the data about the trend lines is quite large.
Furthermore, the spread tends to increase with time (at least for the quantities of
panels b and c), suggesting a significant variability in cloud patterns over the
area, possibly associated to changes in climate.

>>>>

Figure\nobreakspace{}\ref{fig:P-energy} shows the time series of the yearly number of
CE cases (each with duration of one minute), the yearly mean OI and the yearly excess
irradiation for the period 1994 -- 2023, together with corresponding linear trends.
To account for missing data, all three quantities have been divided with the fraction
of the valid GHI observations in each month.  Statistically significant (at the
$95\,\%$ confidence level) increasing trends appear for the yearly number of CE
events
($`r plus_sign(round(yearlyCE[var == "GLB_diff.N", slope], 0))`\pm `r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 0)`\,\text{cases}/\text{year}$)
and the excess irradiation
($`r plus_sign(round(yearlyCE[var == "GLB_diff.sum", slope], 1))` \pm `r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kJ}/\text{year}$),
while the the trend in the yearly mean OI is negligible
($`r plus_sign(round(yearlyCE[var == "GLB_diff.mean", slope], 2))`\pm `r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 1)`\,\text{W}/\text{m}^2/\text{year}$)
and of no statistical significance.
The average OI for the entire period is
$`r plus_sign(round(mean(ST_E_yearly$GLB_diff.mean), 1))`\pm `r round(sd(ST_E_yearly$GLB_diff.mean),1)`\,\text{W}/\text{m}^2$.
The interannual variability of the data about the trend lines is quite large.
Furthermore, the spread tends to increase with time (at least for the quantities of
panels b and c), suggesting a significant variability in cloud patterns over the
area, possibly associated to changes in climate.

### 2024-09-08 article/article.tex
Commit 2024-09-08 08:14

In addition, we provide in Figure\nobreakspace{}\ref{fig:example-year}
an example scatter plot between the measured GHI and the modeled
cloud-free irradiance for one year (2005), where the CE and ECE events
are clearly grouped above the cloud-free irradiance (approximated with
the green line). (Figure\nobreakspace{}\ref{fig:example-year}).

@@

Figure\nobreakspace{}\ref{fig:P-energy} shows the time series of the
yearly number of CE cases (each with duration of one minute), the yearly
mean OI and the yearly excess irradiation for the period 1994 -- 2023,
together with corresponding linear trends. To account for missing data
all three quantities have been divided with the fraction of the valid
GHI observations in each month. All three quantities show increasing
trends, most pronounced for the frequency of occurrence
(\(+111\pm 27\,\text{cases}/\text{year}\)) and the excess irradiation
(\(+325.2 \pm 88\,\text{kJ}/\text{year}\)), which are also statistically
significant. In contrast the trend of the yearly mean OI is negligible
(\(+0.14\pm 0.1\,\text{W}/\text{m}^2/\text{year}\)) and of no
statistical significance. The average OI for the entire period is
\(+42.6\pm 2.8\,\text{W}/\text{m}^2\). The interannual variability of
the data about the trend lines is quite large. Furthermore, the spread
tends to increase with time (at least for the quantities of panels b and
c), suggesting a significant variability in cloud patterns over the
area, possibly associated to changes in climate.

>>>>

In addition, we provide in Figure\nobreakspace{}\ref{fig:example-year}
an example scatter plot between the measured GHI and the modeled
cloud-free irradiance for one year (2005), where the CE and ECE events
are clearly grouped above the cloud-free irradiance (approximated with
the green line).

@@

Figure\nobreakspace{}\ref{fig:P-energy} shows the time series of the
yearly number of CE cases (each with duration of one minute), the yearly
mean OI and the yearly excess irradiation for the period 1994 -- 2023,
together with corresponding linear trends. To account for missing data,
all three quantities have been divided with the fraction of the valid
GHI observations in each month. Statistically significant (at the
\(95\,\%\) confidence level) increasing trends appear for the yearly
number of CE events (\(+111\pm 27\,\text{cases}/\text{year}\)) and the
excess irradiation (\(+325.2 \pm 88\,\text{kJ}/\text{year}\)), while the
the trend in the yearly mean OI is negligible
(\(+0.14\pm 0.1\,\text{W}/\text{m}^2/\text{year}\)) and of no
statistical significance. The average OI for the entire period is
\(+42.6\pm 2.8\,\text{W}/\text{m}^2\). The interannual variability of
the data about the trend lines is quite large. Furthermore, the spread
tends to increase with time (at least for the quantities of panels b and
c), suggesting a significant variability in cloud patterns over the
area, possibly associated to changes in climate.
